### 2011-10-08 docs/src/manual.tex
More option explanations

\item[\fbox{\code{bfs}}]\pindex{bfs}
Similarly to \code{dfs} but use a breadth-first search strategy
to print the values.

\item[\fbox{\code{ids $n$}}]\pindex{ids}
Similarly to \code{dfs} but use an iterative-deepening strategy
with an initial depth bound of $n$. The depth-bound is
duplicated after each iteration.
If $n$ is missing, the default value $n=100$ is used.

\item[\fbox{\code{par $n$}}]\pindex{par}
Similarly to \code{dfs} but use a parallel search strategy
with $n$ threads.
If $n$ is missing, the system chooses an appropriate number
of threads according the current number of available processors.

@@

\item[\fbox{\code{copts $o$}}]\pindex{copts}
Define additional options passed to the KiCS2 compiler.

\item[\fbox{\code{rts $o$}}]\pindex{rts}
Define additional run-time options passed to the Glasgow Haskell Compiler
(by \ccode{+RTS $o$ -RTS}).

>>>>

\item[\fbox{\code{bfs}}]\pindex{bfs}
Similarly to \code{dfs} but use a breadth-first search strategy
to compute and print the values of the given expression.

\item[\fbox{\code{ids}}]\pindex{ids}
Similarly to \code{dfs} but use an iterative-deepening strategy
to compute and print the values of the initial expression.
The initial depth bound is 100 and the depth-bound is
doubled after each iteration.

\item[\fbox{\code{ids $n$}}]\pindex{ids}
Similarly to \code{ids} but use an initial depth bound of $n$.

\item[\fbox{\code{par}}]\pindex{par}
Similarly to \code{dfs} but use a parallel search strategy
to compute and print the values of the initial expression.
The system chooses an appropriate number
of threads according the current number of available processors.

\item[\fbox{\code{par $n$}}]\pindex{par}
Similarly to \code{par} but use $n$ parallel threads.

@@

\item[\fbox{\code{copts $o$}}]\pindex{copts}
Define additional options passed to the KiCS2 compiler.
For instance, setting the option
\startprog
:set copts -O 0
\stopprog
has the effect that all optimizations performed by the KiCS2 compiler
are turned off.

\item[\fbox{\code{rts $o$}}]\pindex{rts}
Define additional run-time options passed to the executable
generated by the Glasgow Haskell Compiler, i.e., the parameters
\ccode{+RTS $o$ -RTS} are passed to the executable.
For instance, setting the option
\startprog
:set rts -H512m
\stopprog
has the effect that the minimum heap size is set to 512 megabytes.
